% Publications - a page listing research articles written using content in the thesis

\pdfbookmark[1]{Publications}{Publications} % Bookmark name visible in a PDF viewer

\chapter*{Publications} % Publications page text

Two contributions have been published as part of the development of this project. Both present some of the results of the \ac{PX} evaluation conducted in this research work.

\bigskip

\noindent Edwin Gamboa, Camilo Ruiz, and Maria Trujillo, "Improving Patient Motivation towards Physical Rehabilitation Treatments with PlayTherapy Exergame." In \textit{Studies in health technology and informatics}. vol 249 (2018), pp. 140-147. ISSN: 0926-9630. URL: \url{http://www.ncbi.nlm.nih.gov/pubmed/29866970}. Presented in \textit{15th International Conference on Wearable, Micro and Nano Technologies for Personalized Health (pHealth 2018)}, 12-14 June 2018, Gjøvik, Norway. Awarded as \textit{Young Scientist Best Paper}
\\\\
Camilo Ruiz, Edwin Gamboa, Andres Cortes, and Maria Trujillo, "Addressing Motivation Issues in Physical Rehabilitation Treatments Using Exergames." In \textit{Serrano C. J., Martínez-Santos J. (eds) Advances in Computing. CCC 2018. Communications in Computer and Information Science}, vol 885. Springer, Cham, (2018), pp. 459-470. ISBN: 978-3-319-98998-3 URL: \url{https://link.springer.com/chapter/10.1007\%2F978-3-319-98998-3_35}. Presented in \textit{13th Colombian Conference on Computing (13CCC)}, 24-26 September 2008, Cartagena, Colombia. Awarded as \textit{Best paper presentation}